Security Audit of Safeplug

### 2014-01-14 procedure.tex
proc

\section{Procedure}
\label{sec:procedure}
TODO: Anna
Safeplug is not open source, which makes a security audit much more challenging.  This leads to a debate on where a user will put his/her trust.  Despite not having the source code, we hope to get a Safeplug, set it up via their website, and use Wireshark to capture traffic and see what happens.  Wireshark allows us to capture and analyze network data \cite{wireshark}.  We are interested both in the communication between the clients and the Safeplug and between the Safeplug and the outside world.

>>>>

\section{Procedure}
\label{sec:proc}
Although Safeplug uses open source components (not that they are properly documented, as we discovered in Section \ref{tos} below), the device itself is not open source, which makes a security audit much more challenging.  We approached this audit both from the perspective of a user (see Section \ref{sec:ux}) and the perspective of a security researcher (Section \ref{sec:tear} - \ref{sec:SSH}).  This included a teardown of one of the boxes to identify components, capturing network traffic, and accessing the box via SSH.

We set up a mock ``home network'' such as the device might be expected to see and then capture traffic both inside that network and between the network and the internet.  We did this by using a computer with two network cards.  One card was connected to a Netgear switch and served as a gateway, DHCP server, and DNS server.  The other card was the connection to the internet.  Setting up the various components, as well as a bridge and IP forwarding across the two network cards was a particularly time-consuming endeavour, but it allowed us to capture Safeplug traffic as it might occur in the wild.  We used Wireshark to analyze the network data that we captured \cite{wireshark}.  We are interested both in the communication between the clients and the Safeplug and between the Safeplug and the outside world.

We expected the SSH component of the project to be a challenge, but thanks to Pogoplug's lack of security, the instructions and root password were available online!  We analyzed the filesystem on the Safeplug discovered an RPC server that was subject to attack from insiders and potentially from external threats as well.

### 2014-01-14 report.tex
modified the paper to include sections
margins
paper additions
Most of the resultsSoftware section
proc

\documentclass[12pt, letterpaper]{article}

@@

>>>>

\documentclass[12pt, letterpaper]{article}
\usepackage[hyphens]{url}
\usepackage{breakurl}
\usepackage[pdftex]{graphicx}
\usepackage[left=1in,top=1in,right=1in,bottom=1in,head=.5in,foot=.5in]{geometry}
\usepackage{setspace}

%\usepackage{caption}
\usepackage{subcaption}
%\usepackage[small,compact]{titlesec}
\usepackage{listings}
\lstnewenvironment{fileName}{%
\lstset{%
        basicstyle=\ttfamily,
        breaklines,
    }%
}{%
}

@@

\input{intro}
\input{goals}
\input{procedure}
\input{results}
\input{resultsSoftware}
\input{related}
\input{conclusion}

\section{Acknowledgements}
We would like to express our gratitude to Josh Kroll for donating a lot of time and his computer to the routing effort.  We also thank whoever left the very nice set of screwdrivers on our desks!

This paper represents our own work in accordance with University regulations.

Anna Kornfeld Simpson and Annie Edmunson

### 2014-01-14 results.tex
smaller figures
proc

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\textwidth]{funnydesc.png}
\caption{This is a figure.}
\label{fig:funnydesc}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\textwidth]{relaydesc.png}
\caption{This is a figure.}
\label{fig:relaydesc}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\textwidth]{instructions}
\caption{This is a figure.}
\label{fig:instructions}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\textwidth]{proxyconfig}
\caption{This is a figure.}
\label{fig:proxyconfig}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=\textwidth]{settings}
\caption{This is a figure.}
\label{fig:settings}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{before}
\caption{This is a figure.}
\label{fig:before}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{after}
\caption{This is a figure.}
\label{fig:after}
\end{center}
\end{figure}

@@

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.25\textwidth]{safeplug_top}
\caption{This is a figure.}
\label{fig:top}
\end{center}
\end{figure}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.25\textwidth]{safeplug_bottom}
\caption{This is a figure.}
\label{fig:bottom}
\end{center}
\end{figure}

>>>>

\begin{figure}[th]
\begin{center}
\includegraphics[width=\textwidth]{funnydesc.png}
\caption{This is a figure.}
\label{fig:funnydesc}
\end{center}
\end{figure}

\begin{figure}[th]
\begin{center}
\includegraphics[width=\textwidth]{relaydesc.png}
\caption{This is a figure.}
\label{fig:relaydesc}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{instructions}
\caption{This is a figure.}
\label{fig:instructions}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{proxyconfig}
\caption{This is a figure.}
\label{fig:proxyconfig}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.75\textwidth]{settings}
\caption{This is a figure.}
\label{fig:settings}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{before}
\caption{This is a figure.}
\label{fig:before}
\end{subfigure}%
\quad
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{after}
\caption{This is a figure.}
\label{fig:after}
\end{subfigure}
\end{figure}

@@

This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.  Although normal use does follow this model of persisting logins across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (German vs Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.

More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  It requires a trip to the browser settings to clear cookies (or not have them set in the first place).  We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}, and future work will include an analysis of this data, particularly looking for third-party cookies.

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[b]{.3\textwidth}
  \includegraphics[width=\textwidth]{safeplug_top}
  \caption{This is a figure.}
  \label{fig:top}
\end{subfigure}%
\qquad
\begin{subfigure}[b]{.3\textwidth}
\includegraphics[width=\textwidth]{safeplug_bottom}
\caption{This is a figure.}
\label{fig:bottom}
\end{subfigure}
\caption{Safeplug circuit board after the teardown.}
\end{figure}
